Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-05-25 edubots_surveys.Rnw
Incorporating into the paper the previous one

In the framework of the EduBots KA2 European project, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms. A \textit{chatbot} is a program, based on Artificial Intelligence techniques, that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language. Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker’s question fluently, and even ask other questions to the human.

The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with. These automatic systems ease personalized learning, 
% Antonio - customized instead personalized? we are repeating 'personalized' twice in a sentence...
adapting individuals' pace of learning, who get personalized online tutoring outside the classroom. Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.

@@

Given the potential advantages that chatbots could bring to the classroom, as a previous step, we created two surveys for bachelor and master degree students at the University of Granada (Spain), which were answered by more than 250 pupils. The obtained results were analysed in \cite{MoraChatbos2021} aiming to identify students' actual needs. The survey asked about their preferences on tools/applications for chatting and messaging, how do they use them in the educational context, who do they like to be in the class messaging groups, and what do they expect bots and chatbots to do to aid them for learning. The conclusions show that students prefer to use known messaging applications, such as Telegram or WhatsApp, mainly to communicate in groups including both classmates and teachers, and they expect chatbots to ease their subject organisation, such as calendar bots, as well as bots to provide grades and subject material.

% Maybe move it to a different place later
In the present work we aim to complement this study with the other main community of the educational process, i.e. teachers. Thus, we have performed a survey among 300 teachers asking about their attitudes towards the use of bots or chatbots in their classes. We analyse their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
\item{ RQ2 - Which kind of chatbots would teachers find useful in their classes?? }
\item{ RQ3 - Which kind of interaction do teachers prefer with their students? }

>>>>

In the framework of the EduBots KA2 European project, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms. A \textit{chatbot} is a program, sometimes based on Artificial Intelligence techniques, that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language. Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker’s question fluently, and even ask other questions to the human. However, in most cases a simple messaging-application attached bot will help the students (and teachers); neither computational intelligence nor comprehension of natural languages are requisites, the only one being the fact that they can be accessed from a synchronous conversational application such as the common instant messaging applications used nowadays.

The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with. These automatic systems ease personalized learning, 
% Antonio - customized instead personalized? we are repeating 'personalized' twice in a sentence...
% Antonio, if you don't like something, and it's as non-controversial as this thing, just change it directly. Reviews are OK, corrections are even more OK. - JJ
adapting individuals' pace of learning, who get personalized online tutoring outside the classroom. Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.

@@

Given the potential advantages that chatbots could bring to the classroom, as a previous step, we created two surveys for bachelor and master degree students at the University of Granada (Spain), which were answered by more than 250 students. The obtained results were analysed with the object of identifying students' actual needs, in \cite{MoraChatbos2021}. The survey asked about their preferences on tools/applications for chatting and messaging, how do they use them in the educational context, who do they like to be with in the class messaging groups, and what do they expect bots and chatbots to do to aid them during their learning process. We concluded that students prefer to use known whatever messaging application, such as Telegram or WhatsApp, they are already using. They also they expected chatbots to help them with their scheduling, provide assignment grades and search class material. Only one of the applications mentioned, having them work with frequently asked questions, might actually require some understanding of natural language, although it can be formulated in such a way that is not needed.

% Maybe move it to a different place later
In the present work we aim to complement this study with teachers, who are the ones that actually would need to implement, configure and maybe program chatbots. Thus, we have performed a survey among 300 teachers asking about their attitudes towards the use of bots or chatbots in their classes. We analyse their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
\item{ RQ2 - Which kind of chatbots would teachers find useful in their classes?? }
\item{ RQ3 - Which kind of interaction do teachers prefer with their students? }
